R for Clinical Study Reports and Submission

### 2022-08-12 tlf-assemble.Rmd
fix typo

A CSR needs to include many TLFs. 
After TLFs are created and saved into individual files, 
we need to assemble them into one files in a pre-specified order.

There are two general approach to achieve the goal.

@@

Let's illustrate the idea by using selected TLFs generated from previous chapters. 
Here, we assume files are saved in the `tlf` folder.

@@

The `rtf_assemble1()` function allow you to combine RTF 
source code in individual files into one larger RTF file.

@@

Microsoft Words uses toggle fields to embed files into one Word document. 
The approach is a dynamic link between files by providing the file absolute path.

::: {.rmdnote}
There is a small learning curve to learn how toggle fields work 
in Microsoft Words. 
After you become familiar with the workflow, 
toggle fields can extend your capability to manage large amount of TLFs
in RTF format.
:::

@@

The `rtf_assemble2()` function 
allow you to create a word file with toggle fields as below.
One benefit is to control the page direction of each TLF as below.

@@

After open the generated `.docx` file, 
you will see a blank file, because the file only contain fields
with hyperlinks.

By using `Alt` + `F9` to **display** the fields and you will 
see information similar to the screenshot below.

@@

::: {.rmdnote}
A typical error message is that system can not find the file 
if you only provide relative path. 
Please double check the correct absolute file path is in `INCLUDETEXT` field. 
:::

To test the toggle field, you can right click one `INCLUDETEXT` filed and 
click `Update Field`.

@@

Now you can update all toggle fields to display all TLFs by 
selecting all fields (`Ctrl + A`), then type `F9`. 
We suggest to test one toggle field before updating all of them.

@@

::: {.rmdnote}
If you modify table content in the combined `.docx` file, 
you may get weird table layout if you update all fields within a toggle field. 
To resolve the issue, please remove all `\* MERGEFORMAT` in the filed mode using `Alt + F9` before updating all toggle fields.
:::

After the combined TLF is ready for delivery, 
you can also unlink toggle fields to save table contents, 
because the absolute path may not work by others.  
To unlink toggle fields, you can select all fields (`Ctrl + A`), 
then type `Ctrl + Shift + F9`.

>>>>

After TLFs are created and saved into individual files, 
we need to assemble them into one file in a pre-specified order.

There are two general approaches to achieving the goal.

@@

Let's illustrate the idea by using selected TLFs generated from previous chapters. 
Here, we assume files are saved in the `tlf/` folder.

@@

The `rtf_assemble1()` function allows user to combine RTF 
source code in individual files into one larger RTF file.

@@

Microsoft Words uses toggle fields to embed files into one Word document. 
The approach is a dynamic link between files by providing the absolute file path.

::: {.rmdnote}
There is a slight learning curve to learning how toggle fields work 
in Microsoft Words. 
After you become familiar with the workflow, 
toggle fields can extend your capability to manage a large amount of TLFs
in RTF format.
:::

@@

The `rtf_assemble2()` function 
allows you to create a word file with toggle fields as below.
One benefit is to control the page direction of each TLF as below.

@@

After opening the generated `.docx` file, 
you will see a blank file because the file only contains fields
with hyperlinks.

By using `Alt + F9` to display the fields and you will 
see information similar to the screenshot below.

@@

::: {.rmdnote}
A typical error message is that system can not find the file 
if you only provide a relative path. 
Please double-check that the correct absolute file path is in the `INCLUDETEXT` field. 
:::

To test the toggle field, you can right-click an `INCLUDETEXT` filed and 
click `Update Field`.

@@

Now you can update all toggle fields to display all TLFs by 
selecting all fields (`Ctrl + A`), then type `F9`. 
We suggest testing one toggle field before updating all of them.

@@

::: {.rmdnote}
If you modify table content in the combined `.docx` file, 
you may get a weird table layout if you update all fields within a toggle field. 
To resolve the issue, please remove all `\* MERGEFORMAT` in the filed mode using `Alt + F9` before updating all toggle fields.
:::

After the combined TLF is ready for delivery, 
you can also unlink toggle fields to save table contents, 
because the absolute path may not work for others.  
To unlink toggle fields, you can select all fields (`Ctrl + A`), 
then type `Ctrl + Shift + F9`.
